Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-27 paper/paper.tex
small edit: Jan Willem -> Jan-Willem

\title{Design and Implementation of Probabilistic Programming Language Anglican}
\authorinfo{David Tolpin \and Jan Willem van de Meent \and Hongseok Yang \and Frank Wood}{University of Oxford}{dtolpin@robots.ox.ac.uk \and jwvdm@robots.ox.ac.uk \and hongseok.yang@cs.ox.ac.uk \and fwood@robots.ox.ac.uk}

>>>>

\title{Design and Implementation of Probabilistic Programming Language Anglican}
\authorinfo{David Tolpin \and Jan-Willem van de Meent \and Hongseok Yang \and Frank Wood}{University of Oxford}{dtolpin@robots.ox.ac.uk \and jwvdm@robots.ox.ac.uk \and hongseok.yang@cs.ox.ac.uk \and fwood@robots.ox.ac.uk}
